---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height = 1
)
```

# DreamTheatR

<!-- badges: start -->

<!-- badges: end -->

R color palettes inspired by Dream Theater album artwork. Use these to spice up your plots and you'll have the entire boardroom nodding in 19/16 before you can say **"Metropolis"**.

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("Brent-Rodgers/DreamTheatR")
```

## Usage

```{r example}
library(DreamTheatR)

# See all palettes
names(dt_palettes)
```

## Palettes

### Images and Words (1992)

```{r, images}
dt_palette("Images1")
```

### Falling Into Infinity (1997)

```{r, falling}
dt_palette("Falling1")
```

### Six Degrees of Inner Turbulence (2002)

```{r, sixdegrees}
dt_palette("SixDegrees1")
```

### A Dramatic Turn of Events (2011)

```{r, dramaticturn}
dt_palette("DramaticTurn1")
```

```{r, volcano, fig.height = 5}
pal <- dt_palette("DramaticTurn1", 21, type = "continuous")
image(volcano, col = pal)
```

### A View from the Top of the World (2021)

```{r, viewfromthetop}
dt_palette("ViewFromTheTop1")
```

## Other Stuff

-   Heavily inspired by [Karthik Ram's `wesanderson` package](https://github.com/karthik/wesanderson) and [\@ewenme's `ghibli` package](https://github.com/ewenme/ghibli)
